Lasso_RCI_Response

### 2024-06-25 Lasso_RCI_Response.Rmd
Updated results,tables,figures

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
```

AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
AAQIIpre <- AAQIIpre |>
  mutate(
    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
  )
Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))

AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
AAQIIpost <- AAQIIpost |>
  mutate(
    AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
      AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
  )
Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))

FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
FMMQ_pre <- FMMQ_pre|>
  mutate(
    #reverse code items
    FFMQpre_4R  = 6 - FFMQpre_4_1,
    FFMQpre_5R  = 6 - FFMQpre_5_1,  
    FFMQpre_7R  = 6 - FFMQpre_7_1, 
    FFMQpre_8R  = 6 - FFMQpre_8_1, 
    FFMQpre_11R = 6 - FFMQpre_11_1, 
    FFMQpre_12R = 6 - FFMQpre_12_1,
    FFMQpre_14R = 6 - FFMQpre_14_1,
    FFMQpre_17R = 6 - FFMQpre_17_1,
    FFMQpre_19R = 6 - FFMQpre_19_1,
    FFMQpre_22R = 6 - FFMQpre_22_1,
    FFMQpre_23R = 6 - FFMQpre_23_1,
    FFMQpre_24R = 6 - FFMQpre_24_1,
    #create scales
    Desc_Ex_pre =
        FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
    Non_react_pre = 
        FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
    Observe_inner_pre = 
        FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
    Self_compasion_pre = 
        FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
    Acting_mindful_pre = 
        FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
    FFMQ_pre_total = 
        Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
    )
Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))

FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
FMMQ_post <- FMMQ_post|>
  mutate(
    #reverse code items
    FFMQpost_4R  = 6 - FFMQpost_4_1,
    FFMQpost_5R  = 6 - FFMQpost_5_1,  
    FFMQpost_7R  = 6 - FFMQpost_7_1, 
    FFMQpost_8R  = 6 - FFMQpost_8_1, 
    FFMQpost_11R = 6 - FFMQpost_11_1, 
    FFMQpost_12R = 6 - FFMQpost_12_1,
    FFMQpost_14R = 6 - FFMQpost_14_1,
    FFMQpost_17R = 6 - FFMQpost_17_1,
    FFMQpost_19R = 6 - FFMQpost_19_1,
    FFMQpost_22R = 6 - FFMQpost_22_1,
    FFMQpost_23R = 6 - FFMQpost_23_1,
    FFMQpost_24R = 6 - FFMQpost_24_1,
    #create scales
    Desc_Ex_post =
        FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
    Non_react_post = 
        FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
    Observe_inner_post = 
        FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
    Self_compasion_post = 
        FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
    Acting_mindful_post = 
        FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
    FFMQ_post_total = 
        Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
    )
Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 1 |
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )
summary(as.factor(Mothership$Prev_AdmitID_1))
view(Mothership)
```

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       ))))))
)

@@

JTRCI with less people
```{r}
Mothership_Missing <- Mothership_post |>
  select(
    ID1, 
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post,CUDOS_pre, CUDOS_post, 
    #ACT stuff
    AAQIIpre,AAQIIpost,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, 
    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post, 
    Acting_mindful_post 
  )

@@

```{r}
Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    #ACT stuff
    AAQIIpre, #AAQIIpost,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    Acting_mindful_pre,
    # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    # Acting_mindful_post,
  ))

@@

# Mothership_post <- Mothership_post |>
#   #1. Filter out scores for people not in the program / don't have data
#   filter(!is.na(Days_complete_1)) |>
#   #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
#   filter(!is.na(CUXOS_pre),
#          !is.na(CUXOS_post),
#          CUXOS_pre > 0,
#          CUXOS_post >= 0,
#          !is.na(CUDOS_pre),
#          !is.na(CUDOS_post),
#          CUDOS_pre > 0,
#          CUDOS_post>= 0
#          ) |>
#   mutate(
#     Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
#     Delta_Dep_DC = CUDOS_post - CUDOS_pre,
#     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
#     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
#   )
```

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPRE_coping:rdqPRE_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    AAQIIpre,
    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    Acting_mindful_pre, 
  ))

Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

>>>>

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
```

```{r}
# AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
# AAQIIpre <- AAQIIpre |>
#   mutate(
#     AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
#       AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
#   )
# Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
# 
# AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
# AAQIIpost <- AAQIIpost |>
#   mutate(
#     AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
#       AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
#   )
# Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))
# 
# FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
# FMMQ_pre <- FMMQ_pre|>
#   mutate(
#     #reverse code items
#     FFMQpre_4R  = 6 - FFMQpre_4_1,
#     FFMQpre_5R  = 6 - FFMQpre_5_1,  
#     FFMQpre_7R  = 6 - FFMQpre_7_1, 
#     FFMQpre_8R  = 6 - FFMQpre_8_1, 
#     FFMQpre_11R = 6 - FFMQpre_11_1, 
#     FFMQpre_12R = 6 - FFMQpre_12_1,
#     FFMQpre_14R = 6 - FFMQpre_14_1,
#     FFMQpre_17R = 6 - FFMQpre_17_1,
#     FFMQpre_19R = 6 - FFMQpre_19_1,
#     FFMQpre_22R = 6 - FFMQpre_22_1,
#     FFMQpre_23R = 6 - FFMQpre_23_1,
#     FFMQpre_24R = 6 - FFMQpre_24_1,
#     #create scales
#     Desc_Ex_pre =
#         FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
#     Non_react_pre = 
#         FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
#     Observe_inner_pre = 
#         FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
#     Self_compasion_pre = 
#         FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
#     Acting_mindful_pre = 
#         FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
#     FFMQ_pre_total = 
#         Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
#     )
# Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))
# 
# FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
# FMMQ_post <- FMMQ_post|>
#   mutate(
#     #reverse code items
#     FFMQpost_4R  = 6 - FFMQpost_4_1,
#     FFMQpost_5R  = 6 - FFMQpost_5_1,  
#     FFMQpost_7R  = 6 - FFMQpost_7_1, 
#     FFMQpost_8R  = 6 - FFMQpost_8_1, 
#     FFMQpost_11R = 6 - FFMQpost_11_1, 
#     FFMQpost_12R = 6 - FFMQpost_12_1,
#     FFMQpost_14R = 6 - FFMQpost_14_1,
#     FFMQpost_17R = 6 - FFMQpost_17_1,
#     FFMQpost_19R = 6 - FFMQpost_19_1,
#     FFMQpost_22R = 6 - FFMQpost_22_1,
#     FFMQpost_23R = 6 - FFMQpost_23_1,
#     FFMQpost_24R = 6 - FFMQpost_24_1,
#     #create scales
#     Desc_Ex_post =
#         FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
#     Non_react_post = 
#         FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
#     Observe_inner_post = 
#         FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
#     Self_compasion_post = 
#         FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
#     Acting_mindful_post = 
#         FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
#     FFMQ_post_total = 
#         Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
#     )
# Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))

@@

    # co occuring disorders
    Co_Anx = as.factor(
      ifelse(Anxiety_C == 1 & Mood_D == 1 |
               Anxiety_C == 1 & BPD_P == 1 |
               Anxiety_C == 1 & Substance_D == 1 |
               Anxiety_C == 1 & Trauma_D == 1 |
               Anxiety_C == 1 & Eating_D ==1 |
               Anxiety_C == 1 & Psychotic_D ==1 |
               Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Mood = as.factor(
      ifelse(Mood_C == 1 & Anxiety_D == 1 |
               Mood_C == 1 & BPD_P == 1 |
               Mood_C == 1 & Substance_D == 1 |
               Mood_C == 1 & Trauma_D == 1 |
               Mood_C == 1 & Eating_D ==1 |
               Mood_C == 1 & Psychotic_D ==1 |
               Mood_C == 1 & Somatic_D==1 , 1, 0)),
    Co_BPD = as.factor(
      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
               BPD_Co_C == 1 & Mood_D == 1 |
               BPD_Co_C == 1 & Substance_D == 1 |
               BPD_Co_C == 1 & Trauma_D == 1 |
               BPD_Co_C == 1 & Eating_D ==1 |
               BPD_Co_C == 1 & Psychotic_D ==1 |
               BPD_Co_C == 1 & !BPD_P == 1 |
               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
    Co_Psychotic = as.factor(
      ifelse(Psychotic_C == 1 & Mood_D == 1 |
               Psychotic_C == 1 & BPD_P == 1 |
               Psychotic_C == 1 & Substance_D == 1 |
               Psychotic_C == 1 & Trauma_D == 1 |
               Psychotic_C == 1 & Eating_D ==1 |
               Psychotic_C == 1 & Anxiety_D ==1 |
               Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Eating = as.factor(
      ifelse(Eating_C == 1 & Mood_D == 1 |
               Eating_C == 1 & BPD_P == 1 |
               Eating_C == 1 & Substance_D == 1 |
               Eating_C == 1 & Trauma_D == 1 |
               Eating_C == 1 & Psychotic_D ==1 |
               Eating_C == 1 & Anxiety_D ==1 |
               Eating_C == 1 & Somatic_D ==1, 1, 0)),
    Co_Somatic =  as.factor(
      ifelse(Somatic_C == 1 & Mood_D == 1 |
               Somatic_C == 1 & BPD_P == 1 |
               Somatic_C == 1 & Substance_D == 1 |
               Somatic_C == 1 & Trauma_D == 1 |
               Somatic_C == 1 & Eating_D ==1 |
               Somatic_C == 1 & Anxiety_D ==1 |
               Somatic_C == 1 & Substance_D ==1 |
               Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Substance = as.factor(
      ifelse(Substance_C == 1 & Mood_D == 1 |
               Substance_C == 1 & BPD_P == 1 |
               Substance_C == 1 & Substance_D == 1 |
               Substance_C == 1 & Trauma_D == 1 |
               Substance_C == 1 & Eating_D ==1 |
               Substance_C == 1 & Anxiety_D ==1 |
               Substance_C == 1 & Somatic_D ==1 |
               Substance_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Trauma = as.factor(
      ifelse(Trauma_C == 1 & Mood_D == 1 |
               Trauma_C == 1 & BPD_P == 1 |
               Trauma_C == 1 & Substance_D == 1 |
               Trauma_C == 1 & Eating_D ==1 |
               Trauma_C == 1 & Anxiety_D ==1 |
               Trauma_C == 1 & Somatic_D ==1 |
               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
    Co_Other = as.factor(
      ifelse(
        Co_Substance == 1 |
        Co_Somatic == 1 |
        Co_Eating == 1 |
        Co_Psychotic == 1, 1, 0))
      )
```

@@

#4 Adding it back to mother ship
    Mothership_post <- Mothership_post |>
      mutate(
        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
        CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
        CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
        CUDOS_pre = BL_CUDOS,
        CUXOS_pre = BL_CUXOS,
        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
        CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
        CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
#5 Making some other varaibles
        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
                                      ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
                                      ))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUXOS),NA,
                                                       ifelse(is.na(BL_CUDOS),NA, "Sub Both"
                                                       )))))),
        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
                                      ifelse(is.na(BL_CUXOS),NA, "Subclinical"
                                      ))),
        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
                                      ifelse(is.na(BL_CUDOS),NA, "Subclinical"
                                      ))),
        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
                                        ifelse(is.na(CUXOS_post),NA, "Subclinical"
                                        ))),
        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
                                        ifelse(is.na(CUDOS_post),NA, "Subclinical"
                                        ))),
        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
                                      ifelse(is.na(BL_CUXOS),NA,
                                             ifelse(is.na(BL_CUDOS),NA, "Sub"
                                             )))),
        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
                                  ifelse(BL_CUXOS > 20, "Sig Anx",
                                         ifelse(BL_CUDOS > 20, "Sig Dep",
                                                ifelse(is.na(BL_CUDOS), NA,
                                                       ifelse(is.na(BL_CUXOS), NA, "Subclinical"
                                                       )))))),
      Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
      Delta_Dep_DC = CUDOS_post - CUDOS_pre
)

@@

JTRCI with less people
```{r}
Mothership_Missing <- Mothership_post |>
  select(
    ID1, 
    # RDQ
    # rdqPRE_coping:rdqPRE_wbs,
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post,CUDOS_pre, CUDOS_post, 
    #ACT stuff
    # AAQIIpre,AAQIIpost,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    # Acting_mindful_pre, 
    # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post, 
    # Acting_mindful_post 
  )

@@

```{r}
Mothership_lasso <- Mothership_post |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  #!is.na(Anxiety_Responder),
  ) |>
  select( c(
    ID1,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
    # #ACT stuff
    # AAQIIpre, #AAQIIpost,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
    # Acting_mindful_pre,
    # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
    # Acting_mindful_post,
  ))

@@

# Mothership_post <- Mothership_post |>
#   #1. Filter out scores for people not in the program / don't have data
#   filter(!is.na(Days_complete_1)) |>
#   #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
#   filter(!is.na(CUXOS_pre),
#          !is.na(CUXOS_post),
#          CUXOS_pre > 0,
#          CUXOS_post >= 0,
#          !is.na(CUDOS_pre),
#          !is.na(CUDOS_post),
#          CUDOS_pre > 0,
#          CUDOS_post>= 0
#          ) |>
#   mutate(

#     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
#     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
#   )
```

@@

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    # #ACT stuff
    # AAQIIpre,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    # Acting_mindful_pre, 
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
    #ACT stuff
    # AAQIIpre,
    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
    # Acting_mindful_pre,
